Sagan Ipsum and a Workflow Guide with Make, R, R Markdown, and Some {stevetemplates}

### 2021-03-22 inst/skeleton/ms.Rmd
some manual LaTeX for whether you're doing bookdown or rmarkdown.
Make pandoc.to detection more robust (#10)
`knitr::opts_knit$get("rmarkdown.pandoc.to")` works fine when knitting, but when running interactively, it returns `logical(0)` and breaks lots of the logic that depends on `is_docx` or `is_latex` being true or false. The `pandoc_to()` function in knitr always returns true or false, though, so it works both when knitting and when working interactively

```r
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == "latex"
is_latex
#> logical(0)

is_latex <- knitr::pandoc_to("latex")
is

```{r setup, include=FALSE}
is_docx <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'docx'
is_latex <- knitr::opts_knit$get("rmarkdown.pandoc.to") == 'latex'

@@

\setlength{\parskip}{6pt}

>>>>

```{r setup, include=FALSE}
is_docx <- knitr::pandoc_to("docx")
is_latex <- knitr::pandoc_to("latex")

@@

<!-- This option seems to be more pleasing for rmarkdown::pdf_document() with my templates -->
<!-- \setlength{\parskip}{6pt} -->

<!-- If you're using bookdown, this seems to look better with bookdown::pdf_document2() -->
\setlength{\parskip}{8pt}
\setlength{\parindent}{-0.15in}
\setlength{\leftskip}{0.15in}
\vspace*{-0.35in}
\noindent
\singlespacing
